rang: Reconstructing reproducible R computational environments

### 2023-03-10 paper/paper.qmd
Add postprocessing to clean up the paper #111

---
title: 'rang: Reconstructing reproducible R computational environments'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
abstract: |
  A complete declarative description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating the declarative description for other researchers to automatically reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2001. The declarative description generated by rang satisfies the definition of a reproducible research compendium and can be shared as such. In this contribution, we show how rang can be used to make otherwise unexecutable code, spanning from fields such as computational social science and bioinformatics, executable again. We also provide instructions on how to use rang to construct reproducible and shareable research compendia of current research. The package is currently available from CRAN (https://cran.r-project.org/web/packages/rang/index.html) and GitHub (https://github.com/chainsawriot/rang).
keywords:
  - R
  - reproducibility
  - docker
year: 2023
bibliography: paper.bib
format:
  pdf: default
  arxiv-pdf:
    keep-tex: true
---

>>>>

---
title: 'rang: Reconstructing reproducible R computational environments'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
    email: chung-hong.chan@gesis.org
    corresponding: true
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
abstract: |
  A complete declarative description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating the declarative description for other researchers to automatically reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2001. The declarative description generated by rang satisfies the definition of a reproducible research compendium and can be shared as such. In this contribution, we show how rang can be used to make otherwise unexecutable code, spanning from fields such as computational social science and bioinformatics, executable again. We also provide instructions on how to use rang to construct reproducible and shareable research compendia of current research. The package is currently available from CRAN (https://cran.r-project.org/web/packages/rang/index.html) and GitHub (https://github.com/chainsawriot/rang).
keywords:
  - R
  - reproducibility
  - docker
year: 2023
bibliography: paper.bib
format:
  pdf: default
  plos-pdf:
    keep-tex: true
    journal:
      id: plosone
---
